Quantitative Auditing of AI Fairness with Differentially Private Synthetic Data

### 2025-01-20 paper/paper.tex
minor

These findings have raised significant concerns about the fairness and ethical implications of using such AI systems in critical decision-making processes. Addressing these biases is essential to ensure that AI systems do not perpetuate existing inequalities and instead contribute to a fairer and more just society.

@@

The concept of differential privacy is particularly valuable in scenarios where sensitive information, such as health records or financial data, is involved. For example, a differential privacy mechanism could allow researchers to analyze patterns in patient health data without exposing any single patient's medical history. This approach strikes a balance between data utility and privacy, enabling meaningful analysis while safeguarding individuals against privacy breaches or inference attacks.

@@

Differentially private synthetic data is particularly valuable in sensitive domains like healthcare and finance, enabling researchers to analyze patterns or identify trends without exposing personal details. It also supports fairness auditing by allowing the examination of datasets and models without revealing sensitive attributes. This dual focus on privacy and utility makes it a valuable tool.

>>>>

These findings have raised significant concerns about the fairness and ethical implications of using such AI systems in critical decision-making processes. Addressing these biases is essential to ensure that AI systems do not perpetuate inequalities.

@@

Differential privacy is especially useful in situations that involve sensitive data. For example, a differential privacy mechanism could allow researchers to analyze patterns in patient health data without exposing any single patient's medical history. This approach strikes a balance between data utility and privacy, enabling meaningful analysis while safeguarding individuals against privacy breaches or inference attacks.

@@

Differentially private synthetic data is particularly valuable in sensitive domains like healthcare and criminal justice, enabling researchers to analyze patterns or identify trends without exposing personal details. It also supports fairness auditing by allowing the examination of datasets and models without revealing sensitive attributes. This dual focus on privacy and utility makes it a valuable tool.
